Closed-loop Neuromorphic Benchmarks

### 2015-11-13 paper/paper.tex
Added labelled breakdown of lego robot
Added analysis of EV3 delay

Now that we have this physical example of the task out minimal simulation
benchmark is meant to cover, we can use it to calibrate the parameters of
the simulation.  For example, communication with the EV3 happens around
200Hz, meaning that there must be a delay on the order of 0.005 seconds.  Given
this, we set the delays in the simulation to be uniformly chosen between
0 and 0.01.  Importantly, we do not need to exactly measure the delay in the
EV3 robot --- we just make sure that the minimal simulation covers even worse
cases.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/lego}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lego} Figure \arabic{figure}.}{ A
     simple physical robot embodiment for calibrating the minimal simulation.
     To rotate the central motor to the desired position $q$, enough force
 must be added to $u$ to counteract the weight of the second unused motor.}
\end{figure}

>>>>

Now that we have this physical example of the task out minimal simulation
benchmark is meant to cover, we can use it to calibrate the parameters of
the simulation.  For example, to characterize the communication delay
between the computing hardware and the EV3 robot, we simply measure the number
of times per second we can send a motor command $u$ and read the position of
the motor $q$ per second.  This works because the \texttt{ev3\_link} software
is entirely synchronous and only responds with motor positions when it
processes a command to do so.  This rate of communication averaged 154-156Hz (95\%
bootstrap confidence interval over 100 trials) with a standard deviation of
3.3-4.7Hz (95\% bootstrap C.I.).  This indicates a round-trip
delay on the order of 0.006 seconds.  Given
this, we set the delays in the simulation to be uniformly chosen between
0 and 0.01, so that the minimal simulation covers delay conditions even
worse than those seen in the EV3 robot.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/lego_labelled}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lego} Figure \arabic{figure}.}{ A
     simple physical robot embodiment for calibrating the minimal simulation.
     All components come with the Lego Mindstorms EV3 kit, and are shown on
     the left (2 large motors; 2 1x11 beams; 1 1x13 beam; 12 pins;
     1 EV3 brick; 1 connector cable).
     To rotate the central motor to the desired position $q$, enough force
 must be added to $u$ to counteract the weight of the second unused motor.}
\end{figure}
